### 2021-02-22 input/proposal.tex
a4 not so easy after all

\section{Dynamic partitioning}
\label{sec:proposal}

In this section, we introduce \NAME, (\TODO{stands for}) a reactive
protocol for logical partitioning the cost of which actually depends
on its usage: when the system becomes quiescent, processes eventually
converge to their respective partition and do not require further
communication afterwards.

@@

>>>>

\section{\NAME for Dynamic Partitioning}
\label{sec:proposal}

In this section, we introduce \NAME, (\TODO{stands for}) a reactive
protocol for logical partitioning in autonomous sytems the cost of
which actually depends on its usage: when the system becomes
quiescent, processes eventually converge to their respective partition
and do not require further communication afterwards.

@@

\subsection{Autonomous systems}

Autonomous systems are geo-distributed networks. Heterogenous
communication links. Hierarchy of communication links. Per-object
broadcast.

We leave the link handling to membership protocols~\REF. The ordering
of links can be done based on latency. For instance, from 0 to 100 ms,
rank 0, from 100 to 1s, rank 2 \ldots

\begin{algorithm}
  \input{input/algoaaaa.tex}
  \caption{\label{algo:aaaa}Primitives for general purpose logical
    partitioning in dynamic systems.}
\end{algorithm}

\TODO{Not so easy\ldots}
